---
title: "Admin 1 Survey Data Report"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
## NEED TO SET THIS TO GET THIS FILE LOCATION ##
knitr::opts_knit$set(root.dir = "~/Boston University/COVID_Interventions/covid19-interventions/hit-covid-timeline")
```


```{r read, include=FALSE}
source("source/utils.R")
source("source/data_report_functions.R")
reload_source()
interven_names <- read_csv("intervention_lookup.csv")
long_data <- get_long_data(fresh_pull = FALSE, long_file_path = "generated_data/survey_data_long.csv", remove_names=TRUE)
last_updated_time <- file.info("generated_data/survey_data_long.csv")$mtime
```


```{r cleantable}

## WANT TO RUN THE WHOLE MARKDOWN LIKE A FUNCTION INPUTS: national_input, country_input, admin_input ##

national_input <- FALSE
admin_input <- "USA.1_1"

if(national_input == TRUE){
  admin_tab_initial <- long_data %>% filter(country == country_input,
                                    national_entry == "Yes")
}else{
  admin_tab_initial <- long_data %>% filter(adm1 == admin_input)
}

admin_tab <- admin_tab_initial %>% 
  arrange(record_id) %>%
    left_join(interven_names, by = c("intervention_specific", "intervention")) %>%
    select(record_id, data_entry_by, entry_date = geography_and_intro_timestamp,
           national_entry, country_name, admin1_name, locality = adm_lowest,
           intervention_clean, intervention_specific_clean,
           date_of_update = t_original, status, subpopulation = pop,
           required, enforcement, size, duration, testing_population = test_pop,
           details, date_flag) %>%
  mutate(entry_date = as.Date(entry_date),
         status_flag = status %in% c("open", "no", "no policy", "none", "unrestricted") &
         date_of_update < as.Date("2020/04/15", origin = "1970/01/01"),
         details = substr(details, 1, 100),
         status_simp = ifelse(status %in% c("all", "closed", "complete contact tracing",
                                              "fully restricted", "required", "yes"), 1,
                                ifelse(status %in% c("partial contact tracing",
                                                     "partially closed", "partially restricted",
                                                     "recommended", "some"), 2,
                                       ifelse(status %in% c("open", "no", "no policy",
                                                            "none", "unrestricted"), 3, status))),
           status_simp = factor(status_simp, levels = c(1, 2, 3),
                                labels = c("Strongly Implemented",
                                           "Partially Implemented",
                                           "Not Implemented")),
           subpop_plot = ifelse(!is.na(subpopulation) &
                                subpopulation == "entire population", 
                                          "Entire Population",
                       ifelse(!is.na(subpopulation), "Not Entire Population", "NA")),
          row_id = 1:n())

admin_name <- admin_tab$admin1_name[1]

interven_list <- admin_tab %>%
  filter(!duplicated(intervention_clean)) %>%
  select(`Included Interventions` = intervention_clean)
```

```{r duplicates}

# Finding potential duplicates
dup_cols <- c("intervention_specific_clean", "status", "subpopulation", "required")

dup_rows <- admin_tab %>%
  group_by(intervention_specific_clean, status, subpopulation, required) %>%
  mutate(time_diff = date_of_update - lag(date_of_update)) %>% 
  filter(time_diff < 3) %>%
  select(intervention_specific_clean, status, subpopulation, required)

dup_data <- inner_join(admin_tab, dup_rows, by = dup_cols) %>%
  mutate(duplicate_flag = TRUE) %>%
  select(row_id, duplicate_flag)

admin_tab <- admin_tab %>%
  full_join(dup_data, by = "row_id") %>%
  mutate(any_flag = date_flag | status_flag | duplicate_flag | status == "unknown") %>%
  replace_na(list(any_flag = FALSE, duplicate_flag = FALSE))
```



# Data Summary Report for `r admin_name`

#### As of `r last_updated_time` there have been `r nrow(admin_tab)` intervention updates reported for `r admin_name`. These entries were logged by `r unique(admin_tab$data_entry_by)[!is.na(unique(admin_tab$data_entry_by))]` These updates represent the following intervention sections:

`r kable(interven_list)`


***

Please review the following updates for each intervention and confirm that the information is correct.

#### To report any corrections to this data please use this form [LINK].

In particular as shown in the following table and highlighted through the rest of the report:

* There are `r sum(admin_tab$date_flag == TRUE)` entries where the date of the intervention update is after the date of entry. **Please confirm that these dates are correct.**
    
* There are `r sum(admin_tab$status_flag == TRUE)` entries where the invervention status indicates a relaxing of restrictions before mid April. **Please confirm that these statuses are correct.**

* There are `r sum(admin_tab$status == "unknown")` entries where the intervention status is "unknown". **Please provide the correct status.**

* There are `r sum(admin_tab$duplicate_flag == TRUE)` entries that may be duplicates. **Please confirm that these are unique updates.**


### Table of Entries with Potential Errors (highlighted in following tables)
```{r flagdata}
flag_data <- admin_tab %>%
  filter(any_flag == TRUE) %>%
  mutate(to_check = ifelse(date_flag == TRUE, "Check Date",
                    ifelse(status_flag == TRUE | status == "unknown", "Check Status",
                           "Check Duplicate"))) %>%
  select(record_id, data_entry_by, entry_date, to_check, locality, intervention_specific_clean,
         date_of_update, status, subpopulation, required, size, enforcement,
         testing_population, duration, details) %>%
  select_if(~sum(!is.na(.)) > 0) %>%
  arrange(intervention_specific_clean)

df <- datatable(flag_data,
        class = "display nowrap compact", # style
        rownames = FALSE,
        options = list(
          scrollX = TRUE, # allow user to scroll wide tables horizontally
          pageLength = 30
          )
)
df
```


***

```{r datatable, include = FALSE}
# You need this code to be able to print datatables within a loop
DT::datatable(matrix())
```


```{r interven_df, results='asis', fig.height=3, fig.width=8}

all_int <- interven_list %>% pull(`Included Interventions`)

for(intervention in all_int){
  cat(sprintf("\n\n## %s\n\n", intervention))
  plotdf <- find_interven_info(admin_tab, intervention)
  print(plotdf[[1]])
  cat(knitr::knit_print(plotdf[[2]]))
}
```



***

```{r missing}
interven_miss <- interven_names %>%
  filter(!intervention_clean %in% admin_tab$intervention_clean) %>%
  filter(!duplicated(intervention_clean)) %>%
  select(`Missing Interventions` = intervention_clean)
```

#### There were no entries for the following interventions. **Please confirm that there have been no updates for these intervention sections.**

`r kable(interven_miss)`




